Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-11 paper/paper.tex
Experimental discussion

\paragraph{Problems where both {\sc Brahma} and {\sc Kalashnikov} synthesise minimal programs}
This represent the majority of cases.  A statistical breakdown of this case is shown in Fig~\ref{fig:stats-table}.
{\sc Kalashnikov} performs substantially better than {\sc Brahma} on these tests, and very similarly to
semibiased {\sc Brahma} (an optimisation introduced in~\cite{brahma-icse}).

\paragraph{Problems where {\sc Kalashnikov} is unable to synthesise a program}
This happens in 8 of the 29 cases.  In each case, {\sc Brahma} needs user guidance to synthesise the program.

\paragraph{Problems where {\sc Kalashnikov} synthesises a shorter program than {\sc Brahma}}
This happens in 4 of the 29 cases.  For example p24 in Fig.~\ref{fig:icse-results-table} uses
an obfuscated procedure

>>>>

{\bf {\sc Brahma} and {\sc Kalashnikov} both synthesise minimal programs:}
This represent the majority of cases.  A statistical breakdown of this case is shown in Fig~\ref{fig:stats-table}.
{\sc Kalashnikov} performs substantially better than {\sc Brahma} on these tests, and similarly to
semibiased {\sc Brahma} (an optimisation introduced in~\cite{brahma-icse}).

{\bf {\sc Kalashnikov} is unable to synthesise a program:}
This happens in 8 of the 29 cases.  In each case, {\sc Brahma} needs user guidance to synthesise the program.

{\bf {\sc Kalashnikov} synthesises a shorter program than {\sc Brahma}:}
This happens in 4 of the 29 cases.  For example the specification for p24 of Fig.~\ref{fig:icse-results-table} 
is a segment of obfuscated C code taken from a piece of malware.  The code uses an apparently unbounded loop
to multiply its input by the constant 45.  {\sc Brahma} synthesises an equivalent program consisting of
4 instructions, whereas {\sc Kalashnikov} synthesises the single instruction \texttt{mul x 45}.
